An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
config: intro

In this paper, we present \app, the first automatic verification framework
for general software configurations. \app is based on a collection of powerful learning 
algorithms, that do not necessarily depend on templates. The learning process takes as input a
 large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
but all of the files in the sample need to be of the same type (such as
MySQL or httpd configuration files).
From that sample,
\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.

>>>>

In this paper, we present \app, the first automatic verification framework
for general software configurations. \app is based on a collection of powerful learning 
algorithms, that do not necessarily depend on templates. The learning process takes as input a
 large sample of configuration files. The process is language-agnostic and it works for any type of configuration files, 
but all of the files in the sample need to be of the same type (such as
MySQL or HTTPD configuration files).
From that sample,
\app learns an abundant set of rules specifying various properties that hold on the given sample. The files in the sample might contain
errors -- we are, therefore, using probabilistic learning to derive a set of accurate rules.
